---
title: "Baseline Models"
author: "Sahana Rayan"
date: "2023-10-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# Loading libraries


```{r}
# install.packages("fixest")
library(fixest)
library(tidyverse)
library(spatialreg)
library(geosphere)
library(spdep)
library(sphet)
```

# Loading data set

```{r}
final_data <- read_csv("../data/final_dta_data.csv")
```

# Table 4

## OLS models
OLS Industrial catch
```{r}
ols_model_ic <- feols(conflict100nmi ~ indcatch000 + 0, data = final_data)
vcov_ols_ic <- vcov_conley(ols_model_ic, , lat = "latitude",lon = "longitude", 
                           cutoff = 111, distance = "spherical")
summary(ols_model_ic, vcov = vcov_ols_ic)
vcov_ols_ic
```

OLS model with non industrial catches

```{r}
ols_model_nic <- feols(conflict100nmi ~ nidcatch000 + 0, data = final_data)
vcov_ols_nic <- vcov_conley(ols_model_nic, , lat = "latitude",lon = "longitude", 
                            cutoff = 111, distance = "spherical")
summary(ols_model_nic, vcov = vcov_ols_nic)
vcov_ols_nic
```

OLS model with total catches

```{r}
ols_model_total <- feols(conflict100nmi ~ catch000 + 0, data = final_data)
vcov_ols_total <- vcov_conley(ols_model_total, lat = "latitude",lon = "longitude", 
                              cutoff = 111, distance = "spherical")
summary(ols_model_total, vcov = vcov_ols_total)
vcov_ols_total
```


## Pooled 2SLS models

Pooled 2SLS industrial catch
```{r}
pooled_model_ic <- feols(conflict100nmi ~ 0 | indcatch000 ~ ocean_prd, data = final_data)
vcov_pooled_ic <- vcov_conley(pooled_model_ic, , lat = "latitude",lon = "longitude", 
                           cutoff = 111, distance = "spherical")
summary(pooled_model_ic, vcov = vcov_pooled_ic)
vcov_pooled_ic
```

Pooled 2SLS non industrial catch
```{r}
pooled_model_nic <- feols(conflict100nmi ~ 0 | nidcatch000 ~ ocean_prd, data = final_data)
vcov_pooled_nic <- vcov_conley(pooled_model_nic, , lat = "latitude",lon = "longitude", 
                           cutoff = 111, distance = "spherical")
summary(pooled_model_nic, vcov = vcov_pooled_nic)
vcov_pooled_nic
```

Pooled 2SLS total catch
```{r}
pooled_model_total <- feols(conflict100nmi ~ 0 | catch000 ~ ocean_prd , data = final_data)
vcov_pooled_total <- vcov_conley(pooled_model_total, lat = "latitude",lon = "longitude", 
                           cutoff = 111, distance = "spherical")
summary(pooled_model_total, vcov = vcov_pooled_total)
vcov_pooled_total
```


## fixed effects model 2SLS


fixed  2SLS industrial catch
```{r}
prodummy_part_form <- paste0(paste("prodummy", 1:34, sep = ""), collapse= " + ")
fixed_model_ic <- feols(formula(paste("conflict100nmi ~ 0 + ", prodummy_part_form, 
                                       "| indcatch000 ~ ocean_prd")), 
                         data = final_data)
vcov_fixed_ic <- vcov_conley(fixed_model_ic, lat = "latitude",lon = "longitude", 
                           cutoff = 111, distance = "spherical")
summary(fixed_model_ic, vcov = vcov_fixed_ic)
vcov_fixed_ic[1,1]
```





fixed  2SLS non industrial catch
```{r}
prodummy_part_form <- paste0(paste("prodummy", 1:34, sep = ""), collapse= " + ")
fixed_model_nic <- feols(formula(paste("conflict100nmi ~ 0 + ", prodummy_part_form, 
                                       "| nidcatch000 ~ ocean_prd")), 
                         data = final_data)
print(paste("conflict100nmi ~ 0 + ", prodummy_part_form, "| nidcatch000 ~ ocean_prd"))
vcov_fixed_nic <- vcov_conley(fixed_model_nic, lat = "latitude",lon = "longitude", 
                           cutoff = 111, distance = "spherical")
summary(fixed_model_nic, vcov = vcov_fixed_nic)
vcov_fixed_nic[1,1]
```

fixed  2SLS total catch
```{r}
prodummy_part_form <- paste0(paste("prodummy", 1:34, sep = ""), collapse= " + ")
fixed_model_total <- feols(formula(paste("conflict100nmi ~ 0 + ", prodummy_part_form, 
                                       "| catch000 ~ ocean_prd")), 
                         data = final_data)
vcov_fixed_total <- vcov_conley(fixed_model_total, lat = "latitude",lon = "longitude", 
                           cutoff = "111km", distance = "spherical")
summary(fixed_model_total)
vcov_fixed_total[1,1]
```

fixed  2SLS fatalities total catch
```{r}
prodummy_part_form <- paste0(paste("prodummy", 1:34, sep = ""), collapse= " + ")
fixed_model_fatal <- feols(formula(paste("fatalities100nmi ~ 0 + ", prodummy_part_form, 
                                       "| catch000 ~ ocean_prd")), 
                         data = final_data)
vcov_fixed_fatal <- vcov_conley(fixed_model_fatal, lat = "latitude",lon = "longitude", 
                           cutoff = "111mi")
summary(fixed_model_fatal)
vcov_fixed_fatal[1,1]
```

# Table 3 stuff

## Coeffecients
```{r}
summary(fixed_model_ic, stage = 1)
summary(fixed_model_nic, stage = 1)
summary(fixed_model_total, stage = 1)
```


## KPR stuff
All bad news bears
```{r}
fitstat(fixed_model_ic, type = "kpr")
fitstat(fixed_model_nic, type = "kpr")
fitstat(fixed_model_total, type = "kpr")
```


# Table 5 stuff

## Pull the W matrix
```{r}
final_data_wo_na <- final_data %>% 
  filter(!is.na(final_data$ocean_prd))
W_est <- matrix(rep(0, 742*742), nrow = 742)
for (i in 1:742) {
  for (j in 1:742) {
    if (i != j) {
      W_est[i, j] <- 1/distHaversine(final_data_wo_na[i, 3:4], final_data_wo_na[j, 3:4], r = 3963)
    }
  }
  print(i)
}
```

```{r}
eigen_w <- eigen(W_est)
W_norm <- W_est / max(abs(eigen_w$values))
```



```{r}
spatial_lag_ic <- stsls(conflict100nmi ~ indcatch000, data = final_data_wo_na, listw = mat2listw(W_norm))
```



```{r}
summary(spatial_lag_ic)
```

```{r}
# spatial_lag_ic <- sacsarlm(formula(paste("conflict100nmi ~ 0 + indcatch000 + ", prodummy_part_form)),
#                                    data = final_data_wo_na, listw = mat2listw(W_norm),
#                                    listw2 = mat2listw(W_norm))

# predict(fixed_model_ic, final_data_wo_na)

fixed_model_ic_stage1 <- lm(formula(paste("indcatch000 ~ 0 + ocean_prd + ", prodummy_part_form)),
                                    data = final_data_wo_na)
final_data_wo_na$indcatch000hat <- fixed_model_ic_stage1$fitted.values
```

```{r}

spatial_lag_ic <- gstslshet(formula(paste("conflict100nmi ~ 0 + indcatch000hat + ", prodummy_part_form)),
                                   data = final_data_wo_na, listw = mat2listw(W_norm))

spatial_lag_ic_2 <- sacsarlm(formula(paste("conflict100nmi ~ 0 + indcatch000hat + ", 
                                           prodummy_part_form)),
                                   data = final_data_wo_na, listw = mat2listw(W_norm),
                                   listw2 = mat2listw(W_norm))
spatial_lag_ic_3 <- gstsls(formula(paste("conflict100nmi ~ 0 + indcatch000hat + ", 
                                           prodummy_part_form)),
                                   data = final_data_wo_na, listw = mat2listw(W_norm),
                                   listw2 = mat2listw(W_norm))
```

```{r}
summary(spatial_lag_ic)
```

```{r}
summary(spatial_lag_ic_2)
```

```{r}
summary(spatial_lag_ic_3)
```









