---
title: "Tables 6,7,11"
author: "Marc Brooks"
date: "2023-10-27"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(fixest)
```


#  Setup
```{r all 2015 model setup}
fish_df <- read_csv("../data/final_dta_data.csv")

# filtering for missing values in response 
miss_tot1014 <- !is.na(fish_df$annual_catch1014)
miss_Ind1014 <- !is.na(fish_df$annual_indcatch1014)
miss_NInd1014 <- !is.na(fish_df$annual_nidcatch1014)

# Names of fixed effect variables 
prov_fe_names <- paste0("prodummy", 1:34)


# Creating formulas for each model 
fml_tot1014 <- paste("conflict100nmi ~ 1",
                     paste( prov_fe_names, collapse = " + "),
                     "annual_catch1014 ~ ocp1014mean",
                         #   paste( prov_fe_names, collapse = " + "), collapse = " + "),
                     sep = " | "
                     )
fml_ind1014 <- paste("conflict100nmi ~ 1",
                     paste( prov_fe_names, collapse = " + "),
                     "annual_indcatch1014 ~ ocp1014mean",
                     sep = " | "
                     )
fml_nind1014 <- paste("conflict100nmi ~ 1",
                     paste( prov_fe_names, collapse = " + "),
                     "annual_nidcatch1014 ~ ocp1014mean",
                     sep = " | "
                     )
```


# Table 7 Regressions: Lagged effects of fisheries on the number of conflicts w/in the year.

## 2SLS for conflict in 2015 using total catches 2010-2014
```{r total 2sls 1014-catch}
mod_tot1014 <- feols(formula(fml_tot1014),
                     data=fish_df[miss_tot1014,])
```


```{r summary tot-2sls-1014}
summary(mod_tot1014)
```

```{r summary conely tot-2sls-1014}
summary(mod_tot1014, vcov = vcov_conley(mod_tot1014, 
                                        lat = "latitude", 
                                        lon = "longitude", 
                                        distance = "spherical"))
```

## 2SLS for conflict in 2015 using industrial catches 2010-2014
```{r ind 2sls 1014-catch}
mod_ind1014 <- feols(formula(fml_ind1014), data=fish_df[miss_Ind1014,])
```


```{r summary Ind-2sls-1014}
summary(mod_ind1014)
```

```{r summary conely Ind-2sls-1014}
summary(mod_ind1014, vcov = vcov_conley(mod_ind1014, 
                                        lat = "latitude", 
                                        lon = "longitude", 
                                        distance = "spherical"))
```

## 2SLS for conflict in 2015 using non-industrial catches 2010-2014
```{r Ind 2sls 1014-catch}
mod_nind1014 <- feols(formula(fml_nind1014), data=fish_df[miss_NInd1014,])
```


```{r summary NInd-2sls-1014}
summary(mod_nind1014)
```

```{r summary conely NInd-2sls-1014}
summary(mod_nind1014, vcov = vcov_conley(mod_nind1014, 
                                        lat = "latitude", 
                                        lon = "longitude", 
                                        distance = "spherical"))
```



# Table 7 Regressions: Lagged effects of fisheries on the number of conflicts w/in the year.

```{r July-Dec 2015 model setup}
# Creating formulas for each model 
fml_tot1014_712 <- paste("conflictm712 ~ 1",
                     paste( prov_fe_names, collapse = " + "),
                     "catch000 ~ ocp16",
                         #   paste( prov_fe_names, collapse = " + "), collapse = " + "),
                     sep = " | "
                     )
fml_ind1014_712 <- paste("conflictm712 ~ 1",
                     paste( prov_fe_names, collapse = " + "),
                     "indcatch000 ~ ocp16",
                     sep = " | "
                     )
fml_nind1014_712 <- paste("conflictm712 ~ 1",
                     paste( prov_fe_names, collapse = " + "),
                     "nidcatch000 ~ ocp16",
                     sep = " | "
                     )
```


## 2SLS for conflict in 2015 July-Dec using total catches 2010-2014
```{r total 2sls 1014-712}
mod_tot1014_712 <- feols(formula(fml_tot1014_712), data=fish_df[miss_tot1014,])
```


```{r summary tot-2sls-1014-712}
summary(mod_tot1014_712)
```

```{r summary conely tot-2sls-1014-712}
summary(mod_tot1014_712, vcov = vcov_conley(mod_tot1014_712, 
                                        lat = "latitude", 
                                        lon = "longitude",
                                        cutoff = 111,
                                        distance = "spherical"))
```

## 2SLS for conflict in 2015 July-Dec using industrial catches 2010-2014
```{r ind 2sls 1014-712}
mod_ind1014_712 <- feols(formula(fml_ind1014_712), data=fish_df[miss_Ind1014,])
```


```{r summary Ind-2sls-1014-712}
summary(mod_ind1014_712)
```

```{r summary conely Ind-2sls-1014}
summary(mod_ind1014_712, vcov = vcov_conley(mod_ind1014_712, 
                                        lat = "latitude", 
                                        lon = "longitude", 
                                        cutoff=111,
                                        distance = "spherical"))
```

## 2SLS for conflict in 2015 July-Dec using non-industrial catches 2010-2014
```{r Ind 2sls 1014-712-catch}
mod_nind1014_712 <- feols(formula(fml_nind1014_712), data=fish_df[miss_NInd1014,])
```


```{r summary NInd-2sls-1014-712}
summary(mod_nind1014_712)
```

```{r summary conely NInd-2sls-1014-712}
summary(mod_nind1014_712, vcov = vcov_conley(mod_nind1014_712, 
                                        lat = "latitude", 
                                        lon = "longitude", 
                                        cutoff = 111,
                                        distance = "spherical"))
```



# Table 11 Regressions: Lagged effects of fisheries on the number of conflicts w/in the year.

```{r formulas developmental regions}
# Names of fixed effect variables 
prov_fe_names <- paste0("prodummy", 1:34)


# Creating formulas for each model 
fml_dev <- paste("conflict100nmi ~ 1",
                     paste( prov_fe_names, collapse = " + "),
                     "catch000 ~ ocean_prd",
                         #   paste( prov_fe_names, collapse = " + "), collapse = " + "),
                     sep = " | "
                     )
```



# Regression dev region 1
```{r 2sls dev 1}
mod_dev1 <- feols(formula(fml_dev), data=fish_df[fish_df$devgroup1==1,])
```


```{r summary conely dev1}
summary(mod_dev1, vcov = vcov_conley(mod_dev1, 
                                        lat = "latitude", 
                                        lon = "longitude", 
                                        cutoff = 111,
                                        distance = "spherical"))
```

# Regression dev region 2
```{r 2sls dev 2}
mod_dev2 <- feols(formula(fml_dev), data=fish_df[fish_df$devgroup2==1,])
```


```{r summary conely dev2}
summary(mod_dev2, vcov = vcov_conley(mod_dev2, 
                                        lat = "latitude", 
                                        lon = "longitude", 
                                        cutoff = 111,
                                        distance = "spherical"))
```


# Regression dev region 3
```{r 2sls dev 3}
mod_dev3 <- feols(formula(fml_dev), data=fish_df[fish_df$devgroup3==1,])
```


```{r summary conely dev3}
summary(mod_dev3, vcov = vcov_conley(mod_dev3, 
                                        lat = "latitude", 
                                        lon = "longitude", 
                                        cutoff = 111,
                                        distance = "spherical"))
```


# Regression dev region 4
```{r 2sls dev 4}
mod_dev4 <- feols(formula(fml_dev), data=fish_df[fish_df$devgroup4==1,])
```


```{r summary conely dev4}
summary(mod_dev4, vcov = vcov_conley(mod_dev4, 
                                        lat = "latitude", 
                                        lon = "longitude", 
                                        cutoff = 111,
                                        distance = "spherical"))
```