---
title: "Tables 6,7,11"
author: "Marc Brooks"
date: "2023-10-27"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(fixest)
```


#  Setup
```{r all 2015 model setup}
fish_df <- read_csv("../data/final_dta_data.csv")

# filtering for missing values in response 
miss_tot1014 <- !is.na(fish_df$annual_catch1014)
miss_Ind1014 <- !is.na(fish_df$annual_indcatch1014)
miss_NInd1014 <- !is.na(fish_df$annual_nidcatch1014)

# Names of fixed effect variables 
prov_fe_names <- paste0("prodummy", 1:34)


# Creating formulas for each model 
fml_tot1014 <- paste(paste("conflict100nmi ~ 0 + ",
                     paste( prov_fe_names, collapse = " + "), sep = ""),
                     "annual_catch1014 ~ ocp1014mean",
                         #   paste( prov_fe_names, collapse = " + "), collapse = " + "),
                     sep = " | "
                     )
fml_ind1014 <- paste(paste("conflict100nmi ~ 0 +",
                     paste( prov_fe_names, collapse = " + ")),
                     "annual_indcatch1014 ~ ocp1014mean",
                     sep = " | "
                     )
fml_nind1014 <- paste(paste("conflict100nmi ~ 0 + ",
                     paste( prov_fe_names, collapse = " + ")),
                     "annual_nidcatch1014 ~ ocp1014mean",
                     sep = " | "
                     )
```


```{r create coeff input}
get_coef <- function(coeftab) {
  case_when(
    coeftab[4] < 0.01 ~ paste("$", round(coeftab[1],4),"^{***}$", sep = ""),
    coeftab[4] < 0.05 ~ paste("$", round(coeftab[1],4),"^{**}$", sep = ""),
    coeftab[4] < 0.1 ~ paste("$", round(coeftab[1],4),"^{*}$", sep = ""),
    TRUE ~ as.character(round(coeftab[1],4))
    )
}

get_se <- function(coeftab) {
  paste("(", round(coeftab[1],4), ")", sep = "")
}
```



# Table 6 Regressions: Lagged effects of fisheries on the number of conflicts w/in the year.

```{r table 6 init}
tab6 <- matrix(numeric(11*4), ncol=4)
col1_names <- c(
              "Dependent variable", "",
              "$Industrial catch_{2010-2014}$", "",
              "$Non-industrial catch_{2010-2014}$", "",
              "$Total catch_{2010-2014}$", "",
              "Observations",
              "Province fixed effects",
              "Instrumented"
)

r1_c24 <-c("(1)","(2)", "(3)")
r2_c24 <-paste0(paste0("$", rep("Conflict_{2015}",3)), "$")
r1011_24 <- rep("Yes", 3)

tab6[ ,1]   <- col1_names
tab6[1,2:4] <- r1_c24
tab6[2,2:4] <- r2_c24
tab6[10,2:4] <- r1011_24
tab6[11,2:4] <- r1011_24
```


## 2SLS for conflict in 2015 using total catches 2010-2014
```{r total 2sls 1014-catch}
mod_tot1014 <- feols(formula(fml_tot1014), data=fish_df)
```


```{r summary conely tot-2sls-1014}
fit.tot1014 <- summary(mod_tot1014, vcov = vcov_conley(mod_tot1014, 
                                        lat = "latitude", 
                                        lon = "longitude", 
                                        cutoff = 111,
                                        distance = "spherical"))
```

## 2SLS for conflict in 2015 using industrial catches 2010-2014
```{r ind 2sls 1014-catch}
mod_ind1014 <- feols(formula(fml_ind1014), data=fish_df)
```

```{r summary conely Ind-2sls-1014}
fit.ind1014 <- summary(mod_ind1014, vcov = vcov_conley(mod_ind1014, 
                                        lat = "latitude", 
                                        lon = "longitude", 
                                        cutoff = 111,
                                        distance = "spherical"))
```

## 2SLS for conflict in 2015 using non-industrial catches 2010-2014
```{r Ind 2sls 1014-catch}
mod_nind1014 <- feols(formula(fml_nind1014), data=fish_df[miss_NInd1014,])
```

```{r summary conely NInd-2sls-1014}
fit.nind1014 <- summary(mod_nind1014, vcov = vcov_conley(mod_nind1014, 
                                        lat = "latitude", 
                                        lon = "longitude", 
                                        cutoff = 111,
                                        distance = "spherical"))
```

```{r create table 6}
tab6[3,2] <- get_coef(fit.ind1014$coeftable)
tab6[4,2] <- get_se(fit.ind1014$se)

tab6[5,3] <- get_coef(fit.nind1014$coeftable)
tab6[6,3] <- get_se(fit.nind1014$se)


tab6[7,4] <- get_coef(fit.tot1014$coeftable)
tab6[8,4] <- get_se(fit.tot1014$se)

tab6[9,2:4] <- c(fit.ind1014$nobs, fit.nind1014$nobs, fit.tot1014$nobs)
```


# Table 7 Regressions: Lagged effects of fisheries on the number of conflicts w/in the year.

```{r July-Dec 2015 model setup}
# Creating formulas for each model 
fml_tot1014_712 <- paste(paste("conflictm712 ~ 0 + ",
                     paste( prov_fe_names, collapse = " + ")),
                     "catch000 ~ ocp16",
                         #   paste( prov_fe_names, collapse = " + "), collapse = " + "),
                     sep = " | "
                     )
fml_ind1014_712 <- paste(paste("conflictm712 ~ 0 + ",
                     paste( prov_fe_names, collapse = " + ")),
                     "indcatch000 ~ ocp16",
                     sep = " | "
                     )
fml_nind1014_712 <- paste(paste("conflictm712 ~ 0 + ",
                     paste( prov_fe_names, collapse = " + ")),
                     "nidcatch000 ~ ocp16",
                     sep = " | "
                     )
```



```{r table 7 init}
tab7 <- matrix(numeric(11*4), ncol=4)
col1_names <- c(
              "Dependent variable", "",
              "Industrial catch", "",
              "Non-industrial catch", "",
              "Total catch", "",
              "Observations",
              "Province fixed effects",
              "Instrumented"
)

r1_c24 <-c("(1)","(2)", "(3)")
r2_c24 <-paste0(paste0("$", rep("Conflict_{m7-m12}",3)), "$")
r1011_24 <- rep("Yes", 3)

tab7[ ,1]   <- col1_names
tab7[1,2:4] <- r1_c24
tab7[2,2:4] <- r2_c24
tab7[10,2:4] <- r1011_24
tab7[11,2:4] <- r1011_24
```


## 2SLS for conflict in 2015 July-Dec using total catches 2010-2014
```{r total 2sls 1014-712}
mod_tot1014_712 <- feols(formula(fml_tot1014_712), data=fish_df)
```


```{r summary conely tot-2sls-1014-712}
fit.tot_712 <- summary(mod_tot1014_712, vcov = vcov_conley(mod_tot1014_712, 
                                        lat = "latitude", 
                                        lon = "longitude",
                                        cutoff = 111,
                                        distance = "spherical"))
```

## 2SLS for conflict in 2015 July-Dec using industrial catches 2010-2014
```{r ind 2sls 1014-712}
mod_ind1014_712 <- feols(formula(fml_ind1014_712), data=fish_df)
```

```{r summary conely Ind-2sls-1014}
fit.ind_712 <- summary(mod_ind1014_712, vcov = vcov_conley(mod_ind1014_712, 
                                        lat = "latitude", 
                                        lon = "longitude", 
                                        cutoff=111,
                                        distance = "spherical"))
```

## 2SLS for conflict in 2015 July-Dec using non-industrial catches 2010-2014
```{r Ind 2sls 1014-712-catch}
mod_nind1014_712 <- feols(formula(fml_nind1014_712), data=fish_df)
```


```{r summary conely NInd-2sls-1014-712}
fit.nind_712 <- summary(mod_nind1014_712, vcov = vcov_conley(mod_nind1014_712, 
                                        lat = "latitude", 
                                        lon = "longitude", 
                                        cutoff = 111,
                                        distance = "spherical"))
```

```{r create table 7}
tab7[3,2] <- get_coef(fit.ind_712$coeftable)
tab7[4,2] <- get_se(fit.ind_712$se)

tab7[5,3] <- get_coef(fit.nind_712$coeftable)
tab7[6,3] <- get_se(fit.nind_712$se)


tab7[7,4] <- get_coef(fit.tot_712$coeftable)
tab7[8,4] <- get_se(fit.tot_712$se)

tab7[9,2:4] <- c(fit.ind_712$nobs, fit.nind_712$nobs, fit.tot_712$nobs)
```


# Table 11 Regressions: Lagged effects of fisheries on the number of conflicts w/in the year.

```{r formulas developmental regions}
# Names of fixed effect variables 
prov_fe_names <- paste0("prodummy", 1:34)


# Creating formulas for each model 
fml_dev <- paste(paste("conflict100nmi ~ 0 + ",
                     paste( prov_fe_names, collapse = " + ")),
                     "catch000 ~ ocean_prd",
                         #   paste( prov_fe_names, collapse = " + "), collapse = " + "),
                     sep = " | "
                     )
```



# Regression dev region 1
```{r 2sls dev 1}
mod_dev1 <- feols(formula(fml_dev), data=fish_df[fish_df$devgroup1==1,])
```


```{r summary conely dev1}
summary(mod_dev1, vcov = vcov_conley(mod_dev1, 
                                        lat = "latitude", 
                                        lon = "longitude", 
                                        cutoff = 111,
                                        distance = "spherical"))
```

# Regression dev region 2
```{r 2sls dev 2}
mod_dev2 <- feols(formula(fml_dev), data=fish_df[fish_df$devgroup2==1,])
```


```{r summary conely dev2}
summary(mod_dev2, vcov = vcov_conley(mod_dev2, 
                                        lat = "latitude", 
                                        lon = "longitude", 
                                        cutoff = 111,
                                        distance = "spherical"))
```


# Regression dev region 3
```{r 2sls dev 3}
mod_dev3 <- feols(formula(fml_dev), data=fish_df[fish_df$devgroup3==1,])
```


```{r summary conely dev3}
summary(mod_dev3, vcov = vcov_conley(mod_dev3, 
                                        lat = "latitude", 
                                        lon = "longitude", 
                                        cutoff = 111,
                                        distance = "spherical"))
```


# Regression dev region 4
```{r 2sls dev 4}
mod_dev4 <- feols(formula(fml_dev), data=fish_df[fish_df$devgroup4==1,])
```


```{r summary conely dev4}
summary(mod_dev4, vcov = vcov_conley(mod_dev4, 
                                        lat = "latitude", 
                                        lon = "longitude", 
                                        cutoff = 111,
                                        distance = "spherical"))
```


# Table 12 Regressions: Impact of IUU fishing.

```{r iuu model setup}
# Creating formulas for each model 
fml_tot_iuu <- paste("conflict100nmi ~ 1",
                     paste( prov_fe_names, collapse = " + "),
                     "iuu000 ~ ocean_prd",
                     sep = " | "
                     )
fml_ind_iuu <- paste("conflict100nmi ~ 1",
                     paste( prov_fe_names, collapse = " + "),
                     "ind_iuu000 ~ ocean_prd",
                     sep = " | "
                     )
fml_nind_iuu<- paste("conflict100nmi ~ 1",
                     paste( prov_fe_names, collapse = " + "),
                     "nid_iuu000 ~ ocean_prd",
                     sep = " | "
                     )
```



```{r table 7 init}
tab12 <- matrix(numeric(11*4), ncol=4)
col1_names <- c(
              "Dependent variable", "",
              "Industrial catch", "",
              "Non-industrial catch", "",
              "Total catch", "",
              "Observations",
              "Province fixed effects",
              "Instrumented"
)

r1_c24 <-c("(1)","(2)", "(3)")
r2_c24 <-paste0(paste0("$", rep("Conflict_{m7-m12}",3)), "$")
r1011_24 <- rep("Yes", 3)

tab7[ ,1]   <- col1_names
tab7[1,2:4] <- r1_c24
tab7[2,2:4] <- r2_c24
tab7[10,2:4] <- r1011_24
tab7[11,2:4] <- r1011_24
```



## 2SLS for conflict in 2015 using total iuu
```{r iuu fishing 2sls}
mod_tot_iuu <- feols(formula(fml_tot_iuu), data=fish_df)
```


```{r summary conely tot-iuu}
summary(mod_tot_iuu, vcov = vcov_conley(mod_tot_iuu, 
                                        lat = "latitude", 
                                        lon = "longitude",
                                        cutoff = 111,
                                        distance = "spherical"))
```


## 2SLS for conflict in 2015 using industrial iuu
```{r ind-iuu fishing 2sls}
mod_ind_iuu <- feols(formula(fml_ind_iuu), data=fish_df)
```


```{r summary conely ind-iuu}
summary(mod_ind_iuu, vcov = vcov_conley(mod_ind_iuu, 
                                        lat = "latitude", 
                                        lon = "longitude",
                                        cutoff = 111,
                                        distance = "spherical"))
```


## 2SLS for conflict in 2015 using Non industrial iuu
```{r ind-iuu fishing 2sls}
mod_nind_iuu <- feols(formula(fml_nind_iuu), data=fish_df)
```


```{r summary conely ind-iuu}
summary(mod_nind_iuu, vcov = vcov_conley(mod_nind_iuu, 
                                        lat = "latitude", 
                                        lon = "longitude",
                                        cutoff = 111,
                                        distance = "spherical"))
```

